comgen-outline

### 2017-12-18 paper/case2-habituals.Rmd
edits throughout habituals, refactor main habituals figure

Segmenting the continuous stream of reality into events is a crucial task for cognition.
Once individuated, an event can be categorized as a kind of a event.
For example, the event of Mary smoking at 2:30pm on January the 24th is an instance of *Mary smoking*. 
Generalizations can be said of this event, in the form of *habitual language*: "Mary smokes".

Events are a broad class of entities. 
In our second case study, we focus on habituals about people's behaviors that take the form: \textsc{singular noun phrase} $+$ \textsc{present tense simple verb phrase} (e.g., "Mary smokes cigarettes.").  
Habituals about people doing actions are interesting because a 
Learning about the behaviors of others is useful because it tells us about what that person is like more generally [e.g., @Repacholi1997; @Seiver2013].
When children describe their lives to other, a surprisingly large amount of the langauge produced concerns the actions of people close to them [e.g., "My brother works part-ti8me at the restaurant"; @McGuire1986].
Habitual language about people may be a more conservative form of *trait language* (e.g., "Mary is a smoker.") and convey that behaviors are relatively enduring [@Gelman1999; @Gelman2004].

@@

<!-- We focus on present-tense habitual sentences of the form  -->
To test the generality of our theory, we use the same computational model and follow the same general experimental structure as in the first case study. 
First, we measure the prior distribution over the frequencies for different actions (e.g., how often different people smoke cigarttes; Expt. 2a).
We then measure endorsements of generalizations about events (*habituals*), while manipulating the frequency with which the event occurs (e.g., how often Mary smokes; Expt. 2b), and use our computational model to predict habitual endorsements. 
<!-- We estimate the priors using a novel data-analytic approach that takes advantage of the mixture-model validated in Expt. 1b. -->
By describing novel characters to participants, we are able to directly the manipulate the frequency (feature-probability) with which the referent does the action.
<!-- In addition to directly manipulating the referent feature-probability, these experiments provide the first test of the generality of our theory: It can apply to generalizations about events as well as categories. -->

Finally, if habituals (and generics) are truly language for conveying generalizations, it would be useful for them to reflect a speaker's expectations, not merely her observations. 
Our computational model predicts endorsement rates given a referent-category feature-probability $h$. 
Does $h$ represent the actual, past frequency of the event (e.g., how often Mary has actually smoked in the past month) or the predictive rate of the event in the near future (e.g., how often we should expect Mary to smoke next week)?
We extend our theory by measuring participants' predictions about future frequencies and endorsements of habituals when causal forces intervene on the world (Expt. 2c).
We then use our model to test whether habitual endorsements are based on past frequencies or future expectations.

@@

## Experiment 2a: Measuring the feature-probability prior for events

In this experiment we elicit the prior distributions over frequencies $P(h)$ for different events in order to generate model predictions for corresponding habitual statements (measured in Expt. 2b \& 2c).
For language about the behaviors of people, $P(h)$ represents a language user's background knowledge about the likely frequency of doing the behavior; this can be conceived as a distribution over *different people*, each of whom do the behavior with different rates.
We designed our elicitation task to take advantage of the mixture-model representation of the feature-probability prior used in Expt. 1 (namely: that the distribution over a feature-probability can be represented as a mixture of probabilities from those with a stable causal mechanism that gives rise to the feature and those without such a mechanism).
For background knowledge of people doing actions, we consider again two components^[
  In the case of event knowledge about people, we expect there to be several more than just these two possibilities represented in the prior, corresponding to individuals with different traits or demographics.
  We assume here a simple structure so as to not make the specification of the prior overly complex.
], which we operationalize by *people who have done the action before* and *people who have not the action before*.
We measure how often people do the action, among those who have done it before, as well as the people's beliefs about the how many people have done the action before; we assume for simplicity that people who have never done the action before will rarely do the action.

@@

To construct our stimulus set, we choose actions from five categories of typical human behaviors: eating/consuming food and drug, work, wearing clothing, entertaining activities, and hobbies. 
For each category, we created pairs or triplets of events that shared a superordinate actions (e.g. \emph{eating} caviar vs. peanut butter).
The events were chosen to intuitively cover a range of likely frequencies.
In total, thirty-one events were used.
For a full list the stimulus set, see Table \mht{make table of stimuli}.

@@

For example, one set of prompts read: *How many women have smoked cigarettes before?*; *For a typical woman who has smoked cigarettes before, how frequently does he smoke cigarettes?*
The difference in meaning of these questions was explained to participants on an instructions page before the experimental trials, and tested for recall on a subsequent trial.
<!-- After reading the instructions, participants were asked to recall the two types of questions. -->
They responded to this attention check by selecting an option from a drop-down menu consisting of four options. 
<!-- They did this to test their understanding and attention for each of the two questions. -->
For the experimental trials, we anticipated there to be different beliefs about the frequency of events depending on whether the actor is male or female, so we asked about both genders.
Participants answered both questions for both genders on each slide (4 questions total per slide, order of male / female randomized between-subjects), and every participant completed all 31 items in a randomized order.

<!-- The experiment began by having participants input the names of eight friends, family members, or people they knew well that they could answer some questions about. -->
<!-- Participants were told that these names would only be used to assist them in reasoning through the second part of the experiment.  -->

<!-- In the second phase of the experiment, participants were asked: "For each of the following people, how often does he or she \textsc{do action}?" -->
<!-- Participants had to fill in the blanks in sentences of the form: "\text{friend does action} ___ times per ___". -->
<!-- The first blank was a text box where participants could enter a number. -->
<!-- The second blank was a drop-down menu where participants could select a time interval from the following options: \{week, 2 weeks, month, 2 months, 6 months, year, 2 years, 5 years\} -->
<!-- They completed this task for each of their eight listed friends or family members. -->
<!-- To make the task slightly less tedious, there was an option where participants could set the time window for all eight of their responses. -->

<!-- In order to get sufficient data for actions that are relatively uncommon (e.g., *climbs mountains*, *writes novels*), if participants responded that all of their friends do the action with a frequency of "0 times" (in some interval), a follow-up question appeared that read: "Do you know anybody who has \textsc{done action} before?".  -->
<!-- If they responded "Yes", another follow-up question appeared that read: "How often do you think that person \textsc{does action}?", with the same dependent measure format as before. -->

<!-- Participants completed these elicitation trials for a random subset of 15 items, presented in a randomized order. -->
<!-- The experiment can be viewed at \url{http://stanford.edu/~mtessler/generics-paper/experiments/habituals/priors/friends-and-family-1.html} -->

<!-- \begin{figure*}[t] -->
<!-- \centering -->
<!--   \includegraphics[width=0.84\textwidth]{figs/tj-scatters-3} -->
<!--   \caption{ -->
<!--   Human acceptability judgments as a function of the log frequency of action (left) and speaker $S_2$ model predictions (right) for ninety-three unique items (event \textsc{x} frequency).  -->
<!--   Color denotes target-individual frequency of action (log scale), with lighter colors indicating more frequent actions.  -->
<!--   Actual frequency noted on x-axis for examples (left). -->
<!--   Error bars correspond to 95\% bootstrapped confidence intervals for the participant data and 95\% Bayesian credible intervals for the model predictions.  -->
<!--   Error bars suppressed and points jittered on left facet for visual clarity. -->
<!--   } -->
<!--   \label{fig:tjScatters} -->
<!-- \end{figure*} -->

<!-- #### Data preprocessing -->

@@

@@

To generate feature-probability prior distributions, we built a Bayesian mixture-model for this prior elicitation task, analagous to that used in Case Study 1 (Expt. 1b).
The only difference is that we estimate the mixture component directly from responses to Question 1. 
We assume that those who have not done the action before will probably not do the action in the future. 
With these assumptions, the feature-probability distribution is given by:

@@

In this experiment, we elicit human endorsements for generalizations about events (*habituals*) while manipulating the frequency with which the target event occurs.

@@

Each event from Expt. 2a was then paired with between 2 - 4 frequencies, for which the habitual statement would be evaluated. 
The frequencies were chosen specific to each event by simulating predictions of the endorsement model (Eq. \ref{eq:S1}) with the goal of maximizing the variability in endorsements across items.
For example, relatively high frequencies were chosen \mht{(e.g., 3 times every week vs. 2 weeks vs. month)} for an item that was expected to occur rather often (e.g., "runs") because the model predicted that much of the variability in endorsement would occur in this range; for an item was expected to occur infrequently (e.g., "climbs mountains"), lower frequencies were chosen \mht{(e.g., )}.
In total, \mht{93} unique items were created by pairing frequencies with events.

@@

```{r habituals-endorsement}
d.hab.endorsement.catch <- read.csv(paste(project.path, "data/habituals/endorsement/", 
                    "habituals-endorsement-catch_trials.csv", sep = ""))

@@

```{r habituals-fullmodel}
n_chains <- 3
n_samples <- 100000
burn <- n_samples / 2
lg <- 20
model_prefix <- "results-habituals-jointModel-S1-"

# m.hab.samp <- data.frame()
# m.hab.fixed.samp <- data.frame()

for (i in seq(1, n_chains)){
  # mi <- fread(paste(project.path,  "models/habituals/results/",
  #                   model_prefix, "smtncs_habitual-",
  #                   n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
  # m.hab.samp <- bind_rows(m.hab.samp, mi %>% mutate(chain = i))

  # mi.fixed <- fread(paste(project.path,  "models/habituals/results/",
  #                   model_prefix, "smtncs_some-",
  #                   n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
  # mi.fixed <- fread(paste(project.path,  "models/habituals/results/",
  #                         "results-habituals-jointModel-inferFixedThreshold-S1-smtncs_some-100000_burn50000_lag20_chain", i, ".csv", sep = ""))
  # 
  #m.hab.fixed.samp <- bind_rows(m.hab.fixed.samp, mi.fixed %>% mutate(chain = i))
}

@@

# save(m.hab.fixed.samp,
#      file = paste(project.path,  "results-habituals-jointModel-inferFixedThreshold-S1-smtncs_some-100000_burn50000_lag20_2chains.RData", sep = ""))

@@

# load(paste(project.path,  "models/habituals/results/", model_prefix, "some-",
#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
load(paste(project.path,  
           "results-habituals-jointModel-inferFixedThreshold-S1-smtncs_some-100000_burn50000_lag20_2chains.RData", sep = ""))

@@

fixed.hab.params.posterior <-  m.hab.fixed.samp %>% 
  filter(B %in% c("noise", "fixedThreshold")) %>%
  group_by(B) %>% 
  summarize(MAP = estimate_mode(val),
            cred_upper = hdi_upper(val),
            cred_lower = hdi_lower(val))

m.hab.somemodel.endorsement <- m.hab.fixed.samp %>%
  filter(type == 'predictive') %>%
  rename(habitual = B, time_period = D, binned_freq = E) %>%
  group_by(habitual, time_period, binned_freq) %>%
  summarize(MAP = estimate_mode(val),
            cred_upper = hdi_upper(val),
            cred_lower = hdi_lower(val))

@@

habituals.endorsement.models <- bind_rows(
  d.hab.endorse.regression,
  left_join(
    m.hab.endorse.rsa %>% 
    rename(prediction = MAP, prediction_lower = cred_lower, prediction_upper = cred_upper),
    d.hab.endorse.regression %>% 
    select(habitual, time_period, logAnnualRate, mixture)
  )
) %>%
  mutate(src = factor(src, levels = c( 
                                      "some_model",
                                      "habituals_model",
                                      "regression_freq", 
                                      "regression_freq_distinct"
                                     ),
                      labels = c(
                                 "Fixed semantics model",
                                 "Uncertain semantics model",
                                 "Referent frequency alone", "Distinctiveness + referent frequency"
                                 ))) %>%
  ggplot(., aes ( x = prediction, xmin = prediction_lower, xmax = prediction_upper,
                  y = MAP_h, ymin = low, ymax = high, fill = logAnnualRate))+
  geom_abline(intercept = 0, slope = 1, lty = 3)+
  geom_linerange(alpha = 0.15)+
  geom_errorbarh(alpha = 0.15)+
  geom_point(shape = 21, size = 3)+
  scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
  scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
  #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
  coord_fixed()+
  xlab("Model prediction")+
  ylab("Human habitual endorsement")+
  facet_wrap(~src, nrow = 2)+
  theme(legend.position = "bottom")+
  guides(fill = F)
```

@@

habituals.endorsement.insets <- hab.listener.predictions %>% 
    mutate(Parameter = factor(Parameter, levels = c("state_Prior",
                                                  "state_Posterior"
                                                  ),
                            labels = c("Listener Prior (Posterior given Silence)",
                                       "Listener Posterior given Habitual")),
         action = fct_relevel(action,
                                "climbs mountains", "hikes", "runs",
                              "goes to the movies", "smokes cigarettes"
                              ) ) %>%
  ggplot(., aes( x = value, fill = Parameter, color = Parameter, lty = Parameter, alpha = Parameter ))+
  geom_density(aes(y = ..scaled..), adjust = 4, size = 1)+
  facet_wrap(~action, nrow = 1)+
  # geom_text_repel(data = category.text.labels,
  #                 aes(label = category, x = x , y = y),
  #                 inherit.aes = F, color = "#2b83ba")+
  #scale_fill_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
  #scale_color_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
  scale_fill_manual(values = c("#636363", "#d7191c"))+#, "#2b83ba"))+
  scale_color_manual(values = c("#636363", "#d7191c"))+#, "#2b83ba"))+
  scale_alpha_manual(values = c(0.6, 0.4))+#, 0))+
  #scale_linetype_manual(values = c(3, 4, 2, 1))+
  #scale_linetype_manual(values = c(3, 4, 1))+
  #scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
  scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
  xlab("Frequency (log scale)") +
  ylab("Scaled probability density")+
  theme(legend.position = "bottom", legend.title = element_blank(),
        axis.text.x = element_text(angle = 90, vjust = 1))+
      scale_x_continuous(limits = c(-5, 8), 
                     breaks = c(-5, 0, 2.5, 4, 5.9),
                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))

```{r habituals-endorsement-figure, fig.width=11, fig.height=9, fig.cap="Endorsing generalizations about events Top left: Human elicited endorsements for ninety-three habitual sentences as a function of the referent (log) frequency of action. Top right: Model fits for the uncertain semantics speaker model (upper right), a fixed semantics speaker model (upper left), and regression models based on referent (log) frequency alone (lower left) and referent log frequency + distinctiveness (lower right). Bottom: Five example frequency priors and listener posteriors upon hearing the generalization. These distributions are inferred using both data sources from Expts. 2a & 2b.  (analagous to the Bayesian data analytic approach outlined in Figure \\ref{fig:genericsModelDiagram})", cache = F}
grid.arrange(fig.habituals.endorsement.vs.freq, 
             habituals.endorsement.models,
             habituals.endorsement.insets, ncol = 2,
             layout_matrix = cbind(c(1,1,3), c(2,2,3)))
```

<!-- For the six items for which data for characters of both genders were collected for each participant, we analyzed only the data from participants' first presentation of the item. -->
Parallel to our analysis of generic language endorsements, we articulate a set of simple regression models and an alternative to our uncertain-threshold RSA model to better understand the data and the contribution of our model.

@@

In our empirically elicited priors, items differ in their mixture parameter reflecting the proportion of people who have done the action before (Figure \@ref(fig:habituals-prior-figure)).
This could be seen as a measure of the *distinctiveness* of the action, analagous to *cue validity* in the case study of generic langauge.
A plausible alternative hypothesis is thus that some simple combination of frequency and distinctiveness information predicts habitual endorsements. 
Here, we articulate a regression model that uses participants' responses to the question about the mixture parameter $\phi$ (i.e., the proportion of people who have done the action before) as well as frequency to predict habitual endorsement.

@@

## Experiment 2c: Observations vs. Predictions

>>>>

The event of Mary smoking at 2:30pm on January the 24th is an instance of a kind of event: *Mary smoking*. 
Just as with categories, generalization can occur over events of a particular type.
When expressed in language, these generalizations take the form of *habitual language*: "Mary smokes".

Events are a broad class of entities. 
In our second case study, we focus on habituals about people's behaviors that take the form: \textsc{singular noun phrase} $+$ \textsc{present tense simple verb phrase} (e.g., "Mary smokes cigarettes.").  
Learning about the behaviors of others is useful because they tell us about what that person is like more generally [e.g., @Repacholi1997; @Seiver2013].
When children describe their lives to other, a surprisingly large amount of the langauge produced concerns the actions of people close to them [e.g., "My brother works part-time at the restaurant"; @McGuire1986].
Habitual language about people may be a more conservative form of *trait language* (e.g., "Mary is a smoker.") and convey that behaviors are relatively enduring [@Gelman1999; @Gelman2004].

@@

<!-- We focus on present-tense habitual sentences of the form  -->
To test the generality of our theory, we use the same computational model and follow the same general experimental structure as in the first case study. 
First, we measure the prevalence prior distribution for different actions (e.g., how often different people smoke cigarttes; Expt. 2a).
We then measure endorsements of generalizations about events (*habituals*), while manipulating the frequency with which the event occurs (e.g., how often Mary smokes; Expt. 2b), and use our computational model to predict habitual endorsements. 
<!-- We estimate the priors using a novel data-analytic approach that takes advantage of the mixture-model validated in Expt. 1b. -->
By describing novel characters to participants, we are able to directly the manipulate the frequency (prevalence) with which the referent does the action.
<!-- In addition to directly manipulating the referent feature-probability, these experiments provide the first test of the generality of our theory: It can apply to generalizations about events as well as categories. -->

Finally, if habituals (and generics) are truly language for conveying generalizations, it would be useful for them to reflect a speaker's expectations, not merely her observations. 
Our computational model predicts endorsement rates given a referent-prevalence $h$. 
Does prevalence represent the actual, past frequency of the event (e.g., how often Mary has actually smoked in the past month) or the predictive rate of the event in the near future (e.g., how often we should expect Mary to smoke next week)?
We extend our theory by measuring participants' predictions about future frequencies and endorsements of habituals when causal forces intervene on the world (Expt. 2c).
We then use our model to test whether habitual endorsements are based on past frequencies or future expectations.

@@

## Experiment 2a: Measuring the prevalence prior for events

In this experiment we elicit the prior distributions over frequencies for different events in order to generate model predictions for corresponding habitual statements (measured in Expt. 2b \& 2c).
For language about the behaviors of people, $P(h)$ represents a language user's background knowledge about the  frequency of doing the behavior; this can be conceived as a distribution over *different people*, each of whom do the behavior with different rates.
We designed our elicitation task to take advantage of the mixture-model representation of the prevalence prior used in Expt. 1 (namely: that the distribution over prevalence can be represented as a mixture of those with a stable causal mechanism that gives rise to the feature and those without such a mechanism).
For background knowledge of people doing actions, we consider again two components^[
  In the case of event knowledge about people, we expect there to be several more than just these two possibilities represented in the prior, corresponding to individuals with different traits or demographics.
  We assume here a simple structure so as to not make the specification of the prior overly complex.
], which we operationalize by *people who have done the action before* and *people who have not the action before*.
We measure how often people do the action, among those who have done it before, as well as the people's beliefs about the how many people have done the action before; we assume for simplicity that people who have never done the action before will rarely do the action.

@@

To construct our stimulus set, we choose actions from five categories of typical human behaviors: eating/consuming food and drug, work, wearing clothing, entertaining activities, and hobbies. 
For each category, we created pairs or triplets of events that shared a superordinate actions (e.g. \emph{eating} caviar vs. peanut butter).
The events were chosen to intuitively cover a range of likely frequencies.
In total, thirty-one events were used.
For a full list the stimulus set, see \mht{Appendix}.

@@

For example, one set of prompts read: "How many women have smoked cigarettes before?"; "For a typical woman who has smoked cigarettes before, how frequently does he smoke cigarettes?"
The difference in meaning of these questions was explained to participants on an instructions page before the experimental trials and tested for recall on a subsequent trial.
They responded to this attention check by selecting an option from a drop-down menu consisting of four options. 
For the experimental trials, we anticipated there to be different beliefs about the frequency of events depending on whether the actor is male or female, so we asked about both genders.
Participants answered both questions for both genders on each slide (4 questions total per slide, order of male / female randomized between-subjects), and every participant completed all 31 items in a randomized order.

@@

### Data analysis and results

@@

To generate prevalence prior distributions, we built a Bayesian mixture-model for this prior elicitation task, analagous to that used in Case Study 1 (Expt. 1b).
The only difference is that we estimate the mixture component directly from responses to Question 1. 
We assume that those who have not done the action before will probably not do the action in the future. 
With these assumptions, the prevalence distribution is given by:

@@

In this experiment, we elicit human endorsements for generalizations about events (*habituals*; e.g., "Mary smokes cigaerettes") while manipulating the frequency with which the referent-event occurs (e.g., how often Mary smokes cigarettes).

### Method
```{r habituals-endorsement}
d.hab.endorsement.catch <- read.csv(paste(project.path, "data/habituals/endorsement/", 
                    "habituals-endorsement-catch_trials.csv", sep = ""))

@@

Each event from Expt. 2a was then paired with between 2 - 4 frequencies, for which the habitual statement would be evaluated. 
Frequencies were always "3 times every \textsc{time period}" so that the referent character had always completed the event multiple times.
\textsc{time period}s were chosen specific to each event by simulating predictions of the endorsement model (Eq. \ref{eq:S1}) with the goal of maximizing the variability in endorsements across items.
For example, relatively high frequencies were chosen (e.g., three times every week vs. 2 months) for an item that was expected to occur rather often (e.g., "runs") because the model predicted that much of the variability in endorsement would occur in this range; for an item was expected to occur infrequently (e.g., "climbs mountains"), lower frequencies were chosen (e.g., three times every 5 years vs. 2 years).
In total, `r nrow(d.hab.endorsement %>% select(habitual, time_period) %>% distinct())` unique items were created by pairing frequencies with events.

@@

@@

```{r habituals-fullmodel, fig.width = 8}
n_chains <- 3
n_samples <- 100000
burn <- n_samples / 2
lg <- 20
model_prefix <- "results-habituals-jointModel-S1-"

# m.hab.samp <- data.frame()
#  m.hab.fixed.samp <- data.frame()
# 
# for (i in seq(1, n_chains)){
#   # mi <- fread(paste(project.path,  "models/habituals/results/",
#   #                   model_prefix, "smtncs_habitual-",
#   #                   n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
#   # m.hab.samp <- bind_rows(m.hab.samp, mi %>% mutate(chain = i))
# 
#   # mi.fixed <- fread(paste(project.path,  "models/habituals/results/",
#   #                   model_prefix, "smtncs_some-",
#   #                   n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
#   mi.fixed <- fread(paste(project.path,  "models/habituals/results/",
#                           "results-habituals-jointModel-inferFixedThresholdCts-S1-smtncs_some-100000_burn50000_lag20_chain", i, ".csv", sep = ""))
#   #
#   m.hab.fixed.samp <- bind_rows(m.hab.fixed.samp, mi.fixed %>% mutate(chain = i))
# }

@@

# save(m.hab.fixed.samp,
#      file = paste(project.path,  "results-habituals-jointModel-inferFixedThresholdCts-noise-S1-smtncs_some-100000_burn50000_lag20_2chains.RData", sep = ""))

@@

# load(paste(project.path,  "models/habituals/results/", model_prefix, "some-",
#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
# load(paste(project.path,  
#            "results-habituals-jointModel-inferFixedThreshold-S1-smtncs_some-100000_burn50000_lag20_2chains.RData", sep = ""))
load(paste(project.path,  "results-habituals-jointModel-inferFixedThresholdCts-noise-S1-smtncs_some-100000_burn50000_lag20_2chains.RData", sep = ""))

@@

fixed.hab.params.posterior <-  m.hab.fixed.samp %>% 
  filter(B %in% c("noise", "fixedThreshold")) %>%
  group_by(B) %>% 
  summarize(MAP = estimate_mode(val),
            cred_upper = hdi_upper(val),
            cred_lower = hdi_lower(val))
fixed.threshold.hab.posterior <- filter(fixed.hab.params.posterior, B == "fixedThreshold")
fixed.noise.hab.posterior <- filter(fixed.hab.params.posterior, B == "noise")
m.hab.somemodel.endorsement <- m.hab.fixed.samp %>%
  filter(type == 'predictive') %>%
  rename(habitual = B, time_period = D, binned_freq = E) %>%
  group_by(habitual, time_period, binned_freq) %>%
  summarize(MAP = estimate_mode(val),
            cred_upper = hdi_upper(val),
            cred_lower = hdi_lower(val))

@@

md.hab <- bind_rows(
  d.hab.endorse.regression,
  left_join(
    m.hab.endorse.rsa %>% 
    rename(prediction = MAP, prediction_lower = cred_lower, prediction_upper = cred_upper),
    d.hab.endorse.regression %>% 
    select(habitual, time_period, logAnnualRate, mixture)
  )
)

# %>%
#   mutate(src = factor(src, levels = c( 
#                                       "some_model",
#                                       "habituals_model",
#                                       "regression_freq", 
#                                       "regression_freq_distinct"
#                                      ),
#                       labels = c(
#                                  "Fixed semantics model",
#                                  "Uncertain semantics model",
#                                  "Referent frequency alone", 
#                                  "Distinctiveness + referent frequency"
#                                  )))

example.habituals.actions <- separate(data.frame(example.habituals), 
                                      example.habituals, 
                                      into=c("action", "time_period"), sep = "_")$action

example.habituals <- c( 
                       #"wears a watch", "wears socks", 
                       "writes poems", "writes novels",
                      "goes to the movies", "watches space launches",
                      "smokes cigarettes","drinks coffee",
                       "climbs mountains","hikes", "runs"
                       )

md.hab.long <- bind_rows(
  md.hab %>% 
    #filter(habitual %in% example.habituals.actions) %>% 
    filter(habitual %in% example.habituals) %>% 
    select(-low, -high, -MAP_h, -mean, -k, -n, -a, -b),
  md.hab %>%
      filter(habitual %in% example.habituals) %>% 
      select(-mean, -k, -n, -a, -b, -prediction, -prediction_lower, -prediction_upper) %>%
      rename(prediction = MAP_h, prediction_lower = low, prediction_upper = high) %>%
      mutate(src = 'data')  
) %>%
  mutate(time_period = factor(time_period, levels = c("5 years", "2 years", "year",
                                                      "6 months", 
                                                      "2 months", "month", 
                                                      "2 weeks", 
                                                      "week")),
         habitual = factor(habitual, levels = example.habituals
                           #c("runs", "hikes", "climbs mountains", "goes to the movies",
                           #                     "smokes cigarettes")
                           ),
         src = factor(src, levels = c("data",
                                      "regression_freq", 
                                      "regression_freq_distinct",
                                      "some_model",
                                      "habituals_model"
                                     ),
                      labels = c("Human data",
                                 "Referent frequency", 
                                 "Distinctiveness +\n referent frequency",
                                 "Fixed semantics",
                                 "Uncertain semantics"
                                 )))

habituals.endorsement.bars <- ggplot(md.hab.long, aes ( y = prediction, ymin = prediction_lower, ymax = prediction_upper,
                  x = time_period, fill = logAnnualRate))+
  #geom_abline(intercept = 0, slope = 1, lty = 3)+
  #geom_linerange(alpha = 0.15)+
  geom_col(position = position_dodge(), color = 'black', width = 0.7)+
  geom_errorbar(alpha = 0.7, width = 0.3)+
  #geom_point(shape = 21, size = 3)+
  #scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
  scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
  #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
  coord_fixed()+
  ylab("Habitual endorsement")+
  xlab("Frequency")+
  facet_grid(src~habitual, scales = 'free')+
  theme(strip.text.y = element_text(hjust = 0, angle = 0),#, vjust = 1),
        axis.text.x = element_text(vjust = 1, hjust = 1, angle = 45),
        legend.position = "bottom") +
   guides(fill = F)
##habituals.endorsement.bar
#fixed.hab.params.posterior
```

```{r habitual-endorsment-scatters}
#View(md.hab)

habituals.endorsement.models <- md.hab %>% mutate(src = factor(src, levels = c(
                                      "regression_freq", 
                                      "regression_freq_distinct",
                                      "some_model",
                                      "habituals_model"
                                     ),
                      labels = c(
                                 "Referent frequency", 
                                 "Distinctiveness + \n referent frequency",
                                 "Fixed semantics",
                                 "Uncertain semantics"
                                 ) )) %>%
ggplot(., aes ( x = prediction, xmin = prediction_lower, xmax = prediction_upper,
                  y = MAP_h, ymin = low, ymax = high, fill = logAnnualRate))+
  geom_abline(intercept = 0, slope = 1, lty = 3)+
  geom_linerange(alpha = 0.15)+
  geom_errorbarh(alpha = 0.15)+
  geom_point(shape = 21, size = 3)+
  scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
  scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
  #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
  coord_fixed()+
  xlab("Model prediction")+
  ylab("Human endorsement")+
  facet_wrap(~src, nrow = 1, strip.position = "top")+
  guides(fill = guide_colorbar(title = 'log annual rate',
                               ticks = F,
                               title.position="top"))+ 
  theme(strip.text.y = element_blank(),# element_text(angle = 0, hjust= 0),
        legend.direction = 'horizontal',
        #legend.position = c(0.025,0.975),
        #legend.position =c(1,1),
        legend.justification = c(1,1)
        )
#habituals.endorsement.models
```

@@

habituals.endorsement.insets <- hab.listener.predictions %>% 
    mutate(Parameter = factor(Parameter, levels = c("state_Prior",
                                                  "state_Posterior"
                                                  ),
                            labels = c("Prevalence Prior",
                                       "Posterior given Habitual")),
         action = factor(action, levels = example.habituals)
                                #"climbs mountains", "hikes", "runs",
                              #"goes to the movies", "smokes cigarettes"
                              ) %>%
  ggplot(., aes( x = value, fill = Parameter, color = Parameter, lty = Parameter, alpha = Parameter ))+
  geom_density(aes(y = ..scaled..), adjust = 1, size = 1)+
  facet_wrap(~action, nrow = 1)+
  # geom_text_repel(data = category.text.labels,
  #                 aes(label = category, x = x , y = y),
  #                 inherit.aes = F, color = "#2b83ba")+
  #scale_fill_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
  #scale_color_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
  scale_fill_manual(values = c("#636363", "#d7191c"))+#, "#2b83ba"))+
  scale_color_manual(values = c("#636363", "#d7191c"))+#, "#2b83ba"))+
  scale_alpha_manual(values = c(0.6, 0.4))+#, 0))+
  #scale_linetype_manual(values = c(3, 4, 2, 1))+
  #scale_linetype_manual(values = c(3, 4, 1))+
  #scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
  scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
  xlab("Frequency (log scale)") +
  ylab("Scaled probability density")+
  theme(#legend.position = "bottom", 
        legend.title = element_blank(),
        axis.text.x = element_text(angle = 90, vjust = 1),
        axis.title.y = element_text(hjust = 1))+
      scale_x_continuous(limits = c(-5, 8), 
                     breaks = c(-5, 0, 2.5, 4, 5.9),
                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))
```

```{r habituals-endorsement-figure, fig.width = 16, fig.height = 12.5, fig.cap="Endorsing generalizations about events. A: Endorsements for nine events given different frequencies of action by human participants and four models. B: Human elicited endorsements for ninety-three habitual sentences as a function of the referent (log) frequency of action. Top right: Model fits for all ninety-three habitual sentences by each model. C: Nine example frequency priors and posteriors upon hearing the generalization. These distributions are inferred using both data sources from Expts. 2a & 2b.", cache = F}

hab.legend <- get_legend(habituals.endorsement.models)
fig.hab.endorse.bars <- habituals.endorsement.bars +
  theme(plot.margin = unit(c(6,0,6,0), "pt")) #+ ggtitle("prevalence priors")
fig.hab.endorse.scatters <- habituals.endorsement.models +
  theme(plot.margin = unit(c(6,0,6,0), "pt")) # + theme(legend.position="none") #+ ylab("")
fig.hab.endorse.priors <- habituals.endorsement.insets +
  theme(plot.margin = unit(c(18,2,6,6), "pt"))

#+ 
    #theme(strip.text.y = element_blank())#+ ggtitle("Interpreter model posterior")
#p4 <- s1.simulations.scatter + theme(plot.margin = unit(c(18,0,6,6), "pt"))

# fig.gen.endorse.toprow <- plot_grid(fig.gen.endorse.data,
#                                      fig.gen.endorse.models, 
#                                     # align = 'v',
#                                     #  axis = 'l',
#                                     labels = c("A", "B"),
#                                     rel_widths = c(0.9, 1))

#fig.hab.toprow <- 
  plot_grid(fig.hab.endorse.bars, fig.hab.endorse.scatters,
                            # plot_grid(fig.hab.endorse.scatters,hab.legend, nrow = 1, rel_widths = c(0.6,4),
                            #                                 axis = 't', align = 'h'),
                            fig.hab.endorse.priors,
                            labels = c("A", "B", "C"), nrow = 3,
                            axis = 'lr', 
                        align = 'v', 
                            rel_heights = c(3.1, 1.4, 1.2))

# plot_grid(fig.hab.toprow,
#           fig.hab.endorse.priors,
#           labels = c("", "C"), nrow = 2, rel_heights = c(3, 1.3)
#           )

#plot_grid( prow, legend, rel_widths = c(3, .3))

# grid.arrange(fig.habituals.endorsement.vs.freq, 
#              habituals.endorsement.models,
#              habituals.endorsement.insets, ncol = 2,
#              layout_matrix = cbind(c(1,1,3), c(2,2,3)))
```

<!-- For the six items for which data for characters of both genders were collected for each participant, we analyzed only the data from participants' first presentation of the item. -->
Parallel to our analysis of generic language endorsements, we articulate a set of simple regression models and an alternative to our uncertain-threshold endorsement model to better understand the data and the contribution of our model.

@@

In our empirically elicited priors, items differ the proportion of people who have done the action before (the *mixture parameter* of the mixture model; Figure \@ref(fig:habituals-prior-figure)).
This parameter can be viewed as a measure of the *distinctiveness* of the action, analagous to *cue validity* in the case study of generic langauge.
We again construct a regression model that treats endorsement as a linear combination of frequency and distinctiveness information. 
We use participants' responses to the question about the mixture parameter $\phi$ (i.e., the proportion of people who have done the action before) as well as frequency given to participants to predict habitual endorsement.

@@

## Experiment 2c: What is prevalence?
